Fast and Error-Adaptive Count-Distinct Sketch \\for Influence Maximization

### 2021-01-15 paper.tex
Progress

        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_score.pdf}
        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_score.pdf}
        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_score.pdf}\\
    \end{center}
    \caption{Effect of $\epsilon$ parameters on \acro's performance.}\label{fig:parameter-smallmultiples} 
\end{figure*}

@@

@@

Although they can be inferior in terms of influence score, recent IM algorithms are shown to be quite fast compared to conventional simulation-based approaches such as {\sc MixGreedy}. 
% However, in this work, we show that \acro{}, which is a conventional algorithm, can be orders of magnitude faster than {\sc MixGreedy} while keeping the quality of the seed vertices the same. 
Techniques such as using GPUs, sketches for finding set intersections, reverse sampling to estimate influence from a small subset of vertices, and estimating the necessary number of simulations/samples required for each step greatly reduces asymptotic boundaries of execution time~\cite{leskovec2009community, borgs2014maximizing, minutoli2019fast, cohen2014sketch, IPA, IMGPU, curipples}.

@@

Two-phased Influence Maximization({\sc Tim+} )\cite{tim} borrows ideas from RIS but overcomes its limitations with a novel algorithm design. The first phase computes a lower-bound of the maximum expected to spread among all size-k node sets, and then uses the lower-bound to derive a parameter $\theta$. In the second phase, samples $\theta$ random RR sets from G, and then derives a size-k node-set $\hat{S}$ that covers a large number of RR sets.

>>>>

        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_score.pdf}
        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_score.pdf}
        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_score.pdf}\\
    \end{center}
    \caption{Effect of $\epsilon$ parameters on \acro($J=256$, $\epsilon_c=0.02$) performance, using $\tau=18$ threads.}\label{fig:parameter-smallmultiples} 
\end{figure*}    
\begin{figure}[h] 
    \centering
    \includegraphics[width=1\linewidth]{images/converge-performance.pdf}
  \centering \caption{Geometic mean of \acro's performance and results quality on different $\epsilon_c$ parameters. ($J=256,\epsilon_l=0.3,\epsilon_g=0.01,\tau=18$) 
    \label{fig:conv-perf}} 
\end{figure}

@@

Performance characteristics of \acro is very different from its state-of-the-art competitors; \acro's performance directly depends on the diameter of the influence graph, whereas other methods mention in this paper depends on the influence score. Due to reason, we observe highly varying performance speed-up results in tables \ref{tab:timings005}-\ref{tab:timings1}. In exceptional settings, such as Pokec dataset and $w=0.01$ where the diameter of the influence network is 43, \acro loses its edge against its fastest competitor. On the other hand in the same dataset with $w=0.1$, the diameter is 17; \acro is 6 times faster than its nearest competitor.

@@

Although they can be inferior in terms of influence score, recent IM algorithms are shown to be quite fast compared to conventional simulation-based approaches such as {\sc MixGreedy}.

Techniques such as using GPUs\cite{IMGPU,curipples}, sketches for finding set intersections\cite{cohen2014sketch,IPA}, reverse sampling to estimate influence from a small subset of vertices\cite{borgs2014maximizing,minutoli2019fast}, and estimating the necessary number of simulations/samples required for each step greatly reduces asymptotic boundaries of execution time\cite{leskovec2009community}.

@@

Two-phased Influence Maximization({\sc Tim+})\cite{tim} borrows ideas from RIS but overcomes its limitations with a novel algorithm design. The first phase computes a lower-bound of the maximum expected to spread among all size-k node sets, and then uses the lower-bound to derive a parameter $\theta$. In the second phase, samples $\theta$ random RR sets from G, and then derives a size-k node-set $\hat{S}$ that covers a large number of RR sets.
